% !TeX encoding = GB2312
\addcontentsline{toc}{chapter}{\hei {参考文献}} %参考文献加入到中文目录
\addcontentsline{toe}{chapter}{\bfseries Bibliography} %参考文献加入到英文目录
\baselineskip 7mm
\begin{thebibliography}{1000}
\setlength{\parskip}{6pt}

\bibitem{akrivis-19-RK-SAV}
G.~Akrivis, B.~Li, and D.~Li.
\newblock Energy-decaying extrapolated RK-SAV methods for the Allen-Cahn and Cahn-Hilliard equations.
\newblock {\em SIAM J. Sci. Comput.}, 41:A3703--A3727, 2019.

\bibitem{argyris-91-FEM-SG}
J.~Argyris, M.~Haase, and J.C. Heinrich.
\newblock Finite element approximation to two-dimensional sine-Gordon solitons.
\newblock {\em Comput. Meth. Appl. Mech. Eng.}, 86:1--26, 1991.

\bibitem{arnold-89-classical}
V.I. Arnold.
\newblock {\em Mathematical Methods of Classical Mechanics}.
\newblock Springer-Verlag, Berlin Heidelberg, second edition, 1989.

\bibitem{benettin-94-symplectic}
G.~Benettin and A.~Giorgilli.
\newblock On the Hamiltonian interpolation of near-to-the identity symplectic mappings with application to symplectic integration algorithms.
\newblock {\em J. Stat. Phys.}, 74:1117--1143, 1994.

\bibitem{betsch-00-time-FEM}
P.~Betsch and P.~Steinmann.
\newblock Inherently energy conserving time finite elements for classical mechanics.
\newblock {\em J. Comput. Phys.}, 160:88--116, 2000.

\bibitem{luigi-12-Poisson}
L.~Brugnano, M.~Calvo, J.I. Montijano, and L.~R\'andez.
\newblock Energy-preserving methods for Poisson systems.
\newblock {\em J. Comput. Appl. Math.}, 236:3890--3904, 2012.

\bibitem{luigi-18-analysis-EQUIP}
L.~Brugnano, G.~Gurioli, and F.~Iavernaro. 
\newblock Analysis of energy and quadratic invariant preserving (EQUIP) methods.
\newblock {\em J. Comput. Appl. Math.}, 335:51--73, 2018.	

\bibitem{luigi-19-HBVM-KDV}
L.~Brugnano, G.~Gurioli, and Y.J. Sun.
\newblock Energy-conserving Hamiltonian boundary value methods for the numerical solution of the Korteweg-de Vries equation.
\newblock {\em J. Comput. Appl. Math.}, 351:117--135, 2019.

\bibitem{luigi-16-line-integral}
L.~Brugnano and F.~Iavernaro.
\newblock {\em Line Integral Methods for Conservative Problems}.
\newblock Chapman \& Hall/CRC: Boca Raton, FL, USA, 2016.

\bibitem{luigi-12-EQUIP}
L.~Brugnano, F.~Iavernaro, and D.~Trigiante.
\newblock Energy- and quadratic invariants-preserving integrators based upon Gauss collocation formulae.
\newblock {\em SIAM J. Numer. Anal.}, 50: 2897--2916, 2012.

\bibitem{luigi-10-HBVM}
L.~Brugnano, F.~Iavernaro, and D.~Trigiante.
\newblock Hamiltonian boundary value methods (energy preserving discrete line integral methods).
\newblock {\em J. Numer. Anal. Ind. Appl. Math.}, 5:17--37, 2010.

\bibitem{cai-20-MS-linear}
J.X. Cai and J.~Shen.
\newblock Two classes of linearly implicit local energy-preserving approach for general multi-symplectic Hamiltonian PDEs.
\newblock {\em J. Comput. Phys.}, 401:108975, 2020.	

\bibitem{cai-19-SG-NB}
W.J. Cai, C.L. Jiang, Y.S. Wang, and Y.Z. Song.
\newblock Structure-preserving algorithms for the two-dimensional sine-Gordon equation with Neumann boundary conditions.
\newblock {\em J. Comput. Phys.}, 395:166--185, 2019.	

\bibitem{cai-18-PAVF}
W.J. Cai, H.C. Li, and Y.S. Wang.
\newblock Partitioned averaged vector field methods.
\newblock {\em J. Comput. Phys.}, 370:25--42, 2018.	

\bibitem{channell-90-symplectic}
P.J. Channell and C.~Scovel.
\newblock Symplectic integration of Hamiltonian systems. 
\newblock {\em Nonlinearity}, 3:231--259, 1990.

\bibitem{chartier-06-algebraic}
P.~Chartier, E.~Faou, and A.~Murua.
\newblock An algebraic approach to invariant preserving integrators: the case of quadratic and Hamiltonian invariants.
\newblock {\em Numer. Math.}, 103:575--590, 2006.

\bibitem{chen-20-EQUIP-MS}
C.C. Chen, J.L. Hong, C.~Sim, and K.~Sonwu.
\newblock Energy and quadratic invariants preserving (EQUIP) multi-symplectic methods for Hamiltonian wave equations.
\newblock {\em J. Comput. Phys.}, 418:109599, 2020.

\bibitem{chen-02-total-MEM}
J.B. Chen. 
\newblock Total variation in discrete multisymplectic field theory and multisymplectic-energy-momentum integrators.
\newblock {\em Lett. Math. Phys.}, 61:63--73, 2002.

\bibitem{chen-03-total}
J.B. Chen, H.Y. Guo, and K.~Wu. 
\newblock Total variation in Hamiltonian formalism and symplectic-energy integrators.
\newblock {\em J. Math. Phys.}, 44:1688--1702, 2003.

\bibitem{chen-01-MS-Fourier}
J.B. Chen and M.Z. Qin.
\newblock Multi-symplectic Fourier pseudospectral method for the nonlinear Schr\"{o}dinger equation.
\newblock {\em Electron. Trans. Numer. Anal.}, 12:193--204, 2001.

\bibitem{cohen-11-linear-poisson}
D.~Cohen and E.~Hairer.
\newblock Linear energy-preserving integrators for Poisson systems.
\newblock {\em BIT}, 51:91--101, 2011.

\bibitem{cooper-87-RK}
G.J. Cooper.
\newblock Stability of Runge-Kutta methods for trajectory problems.
\newblock {\em IMA J. Numer. Anal.}, 7:1--13, 1987.

\bibitem{dahlby-11-general-framework}
M.~Dahlby and B.~Owren.
\newblock A general framework for deriving integral preserving numerical methods for PDEs.
\newblock {\em SIAM J. Sci. Comput.}, 33:2318--2340, 2011.

\bibitem{vogelaere-56-contact}
R.~De Vogelaere.
\newblock Methods of integration which preserve the contact transformation property of Hamiltonian equations.
\newblock {\em Tech. Report No 4, Dept. Mathem., Univ. of Notre Dame, Notre Dame, Ind.}, 1956.

\bibitem{eidnes-20-local-global-kahan}
S.~Eidnes and L.~Li.
\newblock Linearly implicit local and global energy-preserving methods for PDEs with a cubic Hamiltonian.
\newblock {\em SIAM J. Sci. Comput.}, 42:A2865--A2888, 2020.

\bibitem{feng-85-symplectic}
K.~Feng.
\newblock On difference schemes and symplectic geometry.
\newblock {\em In Feng K, ed. Proc 1984 Beijing Symp Diff Geometry and Diff Equations. Science Press, Beijing}, 1985, 42--58.

\bibitem{feng-qin-10-symplectic}
K.~Feng and M.Z. Qin.
\newblock {\em Symplectic Geometric Algorithms for Hamiltonian Systems}.
\newblock Springer-Verlag/Zhejiang Publishing United Group, Zhejiang Science and Technology Publishing House, Berlin/Hangzhou, 2010.

\bibitem{feng-95-volume}
K.~Feng and Z.J. Shang.
\newblock Volume-preserving algorithms for source-free dynamical systems.
\newblock {\em Numer. Math.}, 71:451--463, 1995.

\bibitem{feng-89-generating}
K.~Feng, H.M. Wu, M.Z. Qin, and D.L. Wang.
\newblock Construction of canonical difference schemes for Hamiltonian formalism via generating functions.
\newblock {\em J. Comput. Math.}, 7:71--96, 1989.

\bibitem{furihata-99-DVD}
D.~Furihata.
\newblock Finite difference schemes for $\partial u/\partial t=(\partial/\partial x)^\alpha\delta {G}/\delta u$ that inherit energy conservation or dissipation property.
\newblock {\em J. Comput. Phys.}, 156:181--205, 1999.

\bibitem{furihata-11-DVD-CHCRC}
D.~Furihata and T.~Matsuo.
\newblock {\em Discrete Variational Derivative Method: A Structure-Preserving Numerical Method for Partial Differential Equations}.
\newblock Chapman \& Hall/CRC:Boca Raton, FL, USA, 2011.

\bibitem{gan-13-SPRK}
S.Q. Gan, Z.J. Shang, and G.~Sun.
\newblock A class of symplectic partitioned Runge-Kutta methods.
\newblock {\em Appl. Math. Lett.}, 26:968--973, 2013.

\bibitem{ge-88-Lie-Poisson}
Z.~Ge and J.E. Marsden.
\newblock Lie-Poisson Hamilton-Jacobi theory and Lie-Poisson integrators.
\newblock {\em Phys. Lett. A}, 133:134--139, 1988.

\bibitem{gong-14-local-global-AVF}
Y.Z. Gong, J.X. Cai, and Y.S.~Wang.
\newblock Some new structure-preserving algorithms for general multi-symplectic formulations of Hamiltonian PDEs.
\newblock {\em J. Comput. Phys.}, 279:80--102, 2014.

\bibitem{gong-17-Fourier-NLS}
Y.Z. Gong, Q. Wang, Y.S. Wang, and J.X. Cai.
\newblock A conservative Fourier pseudo-spectral method for the nonlinear Schr\"{o}dinger equation.
\newblock {\em J. Comput. Phys.}, 328:354--370, 2017.

\bibitem{gong-20-high-stable}
Y.Z. Gong, J.~Zhao, and Q.~Wang.
\newblock Arbitrarily high-order linear energy stable schemes for gradient flow models.
\newblock {\em J. Comput. Phys.}, 419:109610, 2020.

\bibitem{gong-20-high-stable-TC}
Y.Z. Gong, J.~Zhao, and Q.~Wang.
\newblock Arbitrarily high-order unconditionally energy stable schemes for thermodynamically consistent gradient flow models.
\newblock {\em SIAM J. Sci. Comput.}, 42:B135--B156, 2020.

\bibitem{gong-18-IEQ-binary-fluid}
Y.Z. Gong, J.~Zhao, X.G. Yang, and Q.~Wang.
\newblock Fully discrete second-order linear schemes for hydrodynamic phase field models of binary viscous fluid flows with variable densities.
\newblock {\em SIAM J. Sci. Comput.}, 40:B138--B167, 2018.

\bibitem{gonzalez-96-discrete}
O.~Gonzalez.
\newblock Time integration and discrete Hamiltonian systems.
\newblock {\em J. Nonlinear Sci.}, 6:449--467, 1996.

\bibitem{hairer-10-collocation}
E.~Hairer.
\newblock Energy-preserving variant of collocation methods.
\newblock {\em J. Numer. Anal. Ind. Appl. Math.}, 5:73--84, 2010.

\bibitem{hairer-lubich-06-geometric}
E.~Hairer, C.~Lubich, and G.~Wanner.
\newblock {\em Geometric Numerical Integration: Structure-Preserving Algorithms for Ordinary Differential Equations}.
\newblock Springer-Verlag, Berlin, 2nd edition, 2006.

\bibitem{hairer-08-ODE-I}
E.~Hairer, S.P. N\o{}rsett, and G.~Wanner
\newblock {\em Solving Ordinary Differential Equations I: Nonstiff Problems}.
\newblock Springer-Verlag, Berlin, 3nd edition, 2008.

\bibitem{harten-83-Godunov}
A.~Harten, P.D. Lax, and B.~Van Leer.
\newblock On upstream differencing and Godunov-type schemes for hyperbolic conservation law.
\newblock {\em SIAM Rev.}, 25:35--61, 1983.

\bibitem{hong-05-MS-PRK}
J.L. Hong, H.Y. Liu, and G.~Sun.
\newblock The multi-symplecticity of partitioned Runge-Kutta methods for Hamiltonian PDEs.
\newblock {\em Math. Comput.}, 75:167--181, 2005.

\bibitem{hong-08-MS-DW}
J.L. Hong and Y.J. Sun.
\newblock Generating functions of multi-symplectic RK methods via DW Hamilton-Jacobi equations.
\newblock {\em Numer. Math.}, 110:491--519, 2008.

\bibitem{itoh-88-VDQ}
T.~Itoh and K.~Abe.
\newblock Hamiltonian-conserving discrete canonical equations based on variational difference quotients.
\newblock {\em J. Comput. Phys.}, 77:85--102, 1988.

\bibitem{jiang-19-SG-IEQ}
C.L. Jiang, W.J. Cai, and Y.S. Wang.
\newblock A linearly implicit and local energy-preserving scheme for the sine-Gordon equation based on the invariant energy quadratization approach.
\newblock {\em J. Sci. Comput.}, 80:1629--1655, 2019.

\bibitem{jiang-20-CH-SAV-JSC}
C.L. Jiang, Y.Z. Gong, W.J. Cai, and Y.S. Wang.
\newblock A linearly implicit structure-preserving scheme for the Camassa-Holm equation based on multiple scalar auxiliary variables approach.
\newblock {\em J. Sci. Comput.}, 83:20, 2020.

\bibitem{jiang-20-CH-SAV-ANM}
C.L. Jiang, Y.S. Wang, and Y.Z. Gong.
\newblock Arbitrarily high-order energy-preserving schemes for the Camassa-Holm equation
\newblock {\em Appl. Numer. Math.}, 151:85--97, 2020.

\bibitem{kane-99-variational}
C.~Kane, J.E. Marsden, and M.~Ortiz.
\newblock Symplectic-energy-momentum preserving variational integrators.
\newblock {\em J. Math. Phys.}, 40:3353--3371, 1999.

\bibitem{lasagni-88-canonical}
F.M. Lasagni.
\newblock Canonical Runge-Kutta methods.
\newblock {\em Z. Angew. Math. Phys.}, 39:952--953, 1988.

\bibitem{leimkuhler-04-simulating}
B.~Leimkuhler and S.~Reich.
\newblock {\em Simulating Hamiltonian Dynamics}.
\newblock Cambridge University Press, Cambridge, 2004.

\bibitem{li-16-AVF}
H.C. Li, Y.S. Wang, and M.Z. Qin.
\newblock A sixth order averaged vector field method.
\newblock {\em J. Comput. Math.}, 34:479--498, 2016.

\bibitem{li-20-EQUIP-constraint}
L.~Li and D.L. Wang.
\newblock Energy and quadratic invariants preserving methods for Hamiltonian systems with holonomic constraints.
\newblock arXiv preprint arXiv:2007.06338, 2020.

\bibitem{li-95-difference-KG}
S.~Li and L.~Vu-Quoc.
\newblock Finite difference calculus invariant structure of a class of algorithms for the nonlinear Klein-Gordon equation.
\newblock {\em SIAM J. Numer. Anal.}, 32:1839--1875, 1995.

\bibitem{li-14-coefficient-varying}
X.Y. Li, A.G. Xiao, and D.L. Wang.
\newblock Generating function methods for coefficient-varying generalized Hamiltonian systems.
\newblock {\em Adv. Appl. Math. Mech.}, 6:87--116, 2014.

\bibitem{liu-20-ESAV}
Z.G. Liu and X.L. Li.
\newblock The exponential scalar auxiliary variable (E-SAV) approach for phase field models and its explicit computing.
\newblock {\em SIAM J. Sci. Comput.}, 42:4B630--B655, 2020.

\bibitem{makazaga-09-generating}
J.~Makazaga and A.~Murua.
\newblock A new class of symplectic integration schemes based on generating functions.
\newblock {\em Numer. Math.}, 113:631--642, 2009.

\bibitem{marchuk-68-splitting}
G.~Marchuk.
\newblock Some applications of splitting-up methods to the solution of mathematical
physics problems.
\newblock {\em Apl. Mat.}, 13:103--132, 1968.

\bibitem{marsden-01-variational}
J.E. Marsden and M.~West.
\newblock Discrete mechanics and variational integrators.
\newblock {\em Acta Numer.}, 10:357--514, 2001.

\bibitem{marsden-98-multisymplectic}
J.E. Marsden, G.W. Patrick, and S.~Shkoller.
\newblock Multisymplectic geometry, variational integrators, and nonlinear PDEs.
\newblock {\em Commun. Math. Phys.}, 199:351--395, 1998.

\bibitem{marsden-99-symmetry}
J.E. Marsden and T.~Ratiu.
\newblock {\em Introduction to Mechanics and Symmetry}.
\newblock Science Press, New York, second edition, 1999.

\bibitem{matsuo-01-dissipative}
T.~Matsuo and D.~Furihata.
\newblock Dissipative or conservative finite-difference schemes for complex-valued nonlinear partial differential equations.
\newblock {\em J. Comput. Phys.}, 171:425--447, 2001.

\bibitem{mclachlan-99-gradient}
R.I. McLachlan, G.R.W. Quispel, and N.~Robidoux.
\newblock Geometric integration using discrete gradients.
\newblock {\em Philos. Trans. R. Soc. Lond. Ser. A-Math. Phys. Eng. Sci.}, 357:1021--1045, 1999.	

\bibitem{mcLachlan-11-stability}
R.I. McLachlan, Y.J. Sun, and P.S.P. Tse.
\newblock Linear stability of partitioned Runge-Kutta methods.
\newblock {\em SIAM J. Numer. Anal.}, 49:232--263, 2011.

\bibitem{menyuk-84-Hamiltonian}
C.R. Menyuk.
\newblock Some properties of the discrete Hamiltonian method.
\newblock {\em Physica D}, 11:109--129, 1984.

\bibitem{miniati-15-galaxies}
F.~Miniati and A.~Beresnyak.
\newblock Self-similar energetics in large clusters of galaxies.
\newblock {\em Nature}, 523:59--62, 2015.

\bibitem{qiao-19-PR-SAV}
Z.H. Qiao, S.Y. Sun, T. Zhang, and Y.Z. Zhang.
\newblock A new multi-component diffuse interface model with Peng-Robinson equation of state and its scalar auxiliary variable (SAV) approach.
\newblock {\em Commun. Comput. Phys.}, 26:1597--1616, 2019.

\bibitem{qin-92-composition}
M.Z. Qin and W.J. Zhu.
\newblock Construction of higher order symplectic schemes by composition.
\newblock {\em Computing}, 47:309--321, 1992.

\bibitem{quispel-08-AVF}
G.R.W. Quispel and D.I. McLaren.
\newblock A new class of energy-preserving numerical integration methods.
\newblock {\em J. Phys. A-Math. Theor.}, 41:045206, 2008.

\bibitem{reich-99-backward}
S.~Reich.
\newblock Backward error analysis for numerical integrators.
\newblock {\em SIAM J. Numer. Anal.}, 36:1549--1570, 1999.

\bibitem{reich-00-MSRK-wave}
S.~Reich.
\newblock Multi-symplectic Runge-Kutta collocation methods for Hamiltonian wave equations.
\newblock {\em J. Comp. Phys.}, 157:473--499, 2000.

\bibitem{ruth-83-canonical}
R.D. Ruth.
\newblock A canonical integration technique.
\newblock {\em IEEE Trans. Nucl. Sci.}, 30:2669--2671, 1983.

\bibitem{sanzserna-88-RK}
J.M. Sanz-Serna.
\newblock Runge-Kutta schemes for Hamiltonian systems.
\newblock {\em BIT}, 28:877--883, 1988.	

\bibitem{sanzserna-94-Hamiltonian}
J.M. Sanz-Serna and M.P. Calvo.
\newblock {\em Numerical Hamiltonian problems}.
\newblock Chapman \& Hall, London, 1994.

\bibitem{shang-94-generating-volume-JCM}
Z.J. Shang.
\newblock Construction of volume-preserving difference schemes for source-free systems via generating functions. 
\newblock {\em J. Comput. Math.}, 12:265--272, 1994.

\bibitem{shang-94-generating-volume}
Z.J. Shang.
\newblock Generating functions for volume-preserving mappings and Hamilton-Jacobi equations for source-free dynamical Systems.
\newblock {\em Sci. China Ser. A}, 37:1172--1188, 1994.

\bibitem{shen-11-spectral}
J.~Shen, T.~Tang, and L-L. Wang.
\newblock {\em Spectral Methods: Algorithms, Analysis and Applications}.
\newblock Springer-Verlag, Berlin, Heidelberg, 2011.

\bibitem{shen-19-SIAM-REV}
J.~Shen, J.~Xu, and J.~Yang.
\newblock A new class of efficient and robust energy stable schemes for gradient flows.
\newblock {\em SIAM Rev.}, 61:474--506, 2019.

\bibitem{shen-18-SAV}
J.~Shen, J.~Xu, and J.~Yang.
\newblock The scalar auxiliary variablev (SAV) approach for gradient flows.
\newblock {\em J. Comput. Phys.}, 353:407--416, 2018.	

\bibitem{sidorov-02-Lyapunov-Schmidt}
N.~Sidorov, B.~Loginov, A.~Sinitsyn, and M.~Falaleev.
\newblock {\em Lyapunov-Schmidt Methods in Nonlinear Analysis and Applications}.
\newblock Math. Appl. 550, Kluwer Academic, Dordrecht, Netherlands, 2002.

\bibitem{siegel-71-Lectures}
C.~Siegel and J.~Moser.
\newblock {\em Lectures on celestial mechanics}.
\newblock Springer-Verlag, Berlin, 1971.

\bibitem{song-19-coupled}
M.Z. Song, X.~Qian, H.~Zhang, J.M. Xia, and S.H. Song.
\newblock Two kinds of new energy-preserving schemes for the coupled nonlinear Schr\"odinger equations.
\newblock {\em Commun. Comput. Phys.}, 25:1127--1143, 2019.

\bibitem{strang-68-difference}
G.~Strang.
\newblock On the construction and comparison of difference schemes.
\newblock {\em SIAM J. Numer. Anal.}, 5:506--517, 1968.

\bibitem{sun-00-symplectic-RK}
G.~Sun.
\newblock A simple way of constructing symplectic Runge-Kutta methods.
\newblock {\em J. Comput. Math.}, 18:61--68, 2000.

\bibitem{sun-93-symplectic-PRK}
G.~Sun.
\newblock Symplectic partitioned Runge-Kutta methods.
\newblock {\em J. Comput. Math.}, 11:365--372, 1993.

\bibitem{sun-05-Birkhoffian}
Y.J. Sun and Z.J. Shang.
\newblock Structure-preserving algorithms for Birkhoffian systems.
\newblock {\em Phys. Lett. A}, 336:358--369, 2005. 

\bibitem{suris-90-variational}
Y.B. Suris.
\newblock Hamiltonian methods of Runge-Kutta type and their variational interpretation.
\newblock {\em Matem. Mod.}, 2:78--87, 1990.

\bibitem{suzuki-90-decomposition}
M.~Suzuki.
\newblock Fractal decomposition of exponential operators with applications to many-body theories and Monte Carlo simulations.
\newblock {\em Phys. Lett. A}, 146:319--323, 1990.
  
\bibitem{tang-12-time-FEM}
W.S. Tang and Y.J. Sun.
\newblock Time finite element methods: a unified framework for numerical discretizations of ODEs.
\newblock {\em Appl. Math. Comput.}, 219:2158-2179, 2012.

\bibitem{trotter-59-semi-groups}
H.F. Trotter.
\newblock On the product of semi-groups of operators.
\newblock {\em Proc. Amer. Math. Soc.}, 10:545--551, 1959.

\bibitem{tu-19-generating}
X.B. Tu, A.~Murua, and Y.F. Tang.
\newblock New high order symplectic integrators via generating functions with its application in many-body problem.
\newblock {\em BIT}, 4:1--27, 2019.

\bibitem{veselov-91-integrable}
A.P. Veselov.
\newblock Integrable maps.
\newblock {\em Russ. Math. Surv.}, 46:1--51, 1991.

\bibitem{wang-13-parametric-PRK}
D.L. Wang, A.G. Xiao, and X.Y. Li.
\newblock Parametric symplectic partitioned Runge-Kutta methods with energy-preserving properties for Hamiltonian system.
\newblock {\em Comput. Phys. Commun.}, 184: 303--310, 2013.

\bibitem{wang-14-stochastic}
L.J. Wang and J.L. Hong.
\newblock Generating functions for stochastic symplectic methods. 
\newblock {\em Discret. Contin. Dyn. Syst.}, 34:1211--1228, 2014.

\bibitem{wang-13-multisymplectic}
Y.S. Wang and J.L. Hong.
\newblock Multi-symplectic algorithms for Hamiltonian partial differential
equations.
\newblock {\em Commun. Appl. Math. Comput.}, 27:163--230, 2013.

\bibitem{wang-03-sine-Gordon}
Y.S. Wang, B.~Wang, Z.Z. Ji, and M.Z. Qin.
\newblock High order symplectic schemes for the sine-Gordon equation.
\newblock {\em J. Phys. Soc. Jpn.}, 72:2731--2736, 2003.

\bibitem{wang-08-LSP}
Y.S. Wang, B.~Wang, and M.Z. Qin.
\newblock Local structure-preserving algorithms for partial differential
equations.
\newblock {\em Sci. China Ser. A}, 51:2115--2136, 2008.

\bibitem{wu-13-oscillatory}
X.Y. Wu, B.~Wang, and W.~Shi.
\newblock Efficient energy-preserving integrators for oscillatory Hamiltonian systems.
\newblock {\em J. Comput. Phys.}, 235:587--605, 2013.

\bibitem{yang-16-IEQ}
X.F. Yang.
\newblock Linear, first and second-order, unconditionally energy stable numerical schemes for the phase field model of homopolymer blends.
\newblock {\em J. Comput. Phys.}, 327:294--316, 2016.

\bibitem{yang-17-IEQ}
X.F. Yang, J.~Zhao, and Q.~Wang.
\newblock Numerical approximations for the molecular beam epitaxial growth model based on the invariant energy quadratization method.
\newblock {\em J. Comput. Phys.}, 333:104--127, 2017.	

\bibitem{yoshida-90-construction}
H.~Yoshida.
\newblock Construction of higher order symplectic integrators.
\newblock {\em Phys. Lett. A}, 150:262--268, 1990.

\bibitem{zhang-16-charged}
R.L. Zhang, H.~Qin, Y.F. Tang, J.~Liu, H.~Yang, and J.Y. Xiao.
\newblock Explicit symplectic algorithms based on generating functions for charged particle dynamics.
\newblock {\em Phys. Rev. E}, 94:013205, 2016.

\bibitem{zotos-15-HH}
E.E. Zotos.
\newblock Classifying orbits in the classical H{\'e}non--Heiles Hamiltonian system.
\newblock {\em Nonlinear Dyn.}, 79:1665--1677, 2015.

\end{thebibliography}
